A Context Menu for the Real World: Controlling Physical Devices Through Head-Worn Infrared Targeting

### 2013-09-18 doc/sigchi14/interaction.tex
update captions and descriptions for figure interaction

\begin{figure*}[t!]
\centering
\includegraphics[width=7in]{figures/stepbystep}
\caption{Step by step walkthrough of interaction goes here.}
\label{fig:interaction}
\end{figure*}

@@

\subsection{Interaction Flow}
{\bf Look:} Users select a target device by looking in its general direction.
Glass periodically sends a device id through its IR emitter analogous to Patel's approach~\cite{patel_2-way_2003}. Target appliances have IR receivers and offer immediate visual feedback by toggling a red LED whenever a valid id is received (Figure~\ref{fig:interaction}A). This enables {\em scanning} the environment with ones gaze to see which devices can be controlled.

@@

{\bf Control:} Glass displays a user interface for parameters of the chosen device (Figure~\ref{fig:interaction}B). The interface is controlled with the temple-mounted touchpad through the following gesture set: tapping toggles discrete parameters; single finger swipe changes between available parameters; double finger swipe adjusts continuous parameters. This scheme was chosen because the touchpad is only comfortably operable in the coronal plane (front to back) but not in the saggital plane (up and down). 
Control commands are sent over XBee radios.

@@

\subsection{Disambiguation}
Head orientation only indicates a general area of visual interest. It does not necessarily match gaze orientation as extra-ocular muscles can move the eyes. The IR beam of our device also has a certain spread (see next section). In an environment dense with potential targets, multiple targets could be within range. Users can tell when multiple feedback LEDs in the environment illuminate. To disambiguate, users can either move to adjust their head position, or, alternatively, call up a disambiguation dialog on the Glass display. The dialog presents a list filtered to only those devices that are within IR range. Users navigate the list using the touchpad, and then continue their interaction as described above.

>>>>

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/stepbystep.png}
\caption{(A) Glass periodically sends out infrared signal aligned with the direction user is facing. (B) Device toggles red led as visual feedback when receiving valid signals. (C) User taps to connect with responding client}
\label{fig:interaction}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/stepbystep_multi.png}
\caption{(A) Multiple clients are within range. (B) All responding clients lights up blue led while the current hovered one blinks. (C) swipe the touchpad to traverse between responding devices. }
\label{fig:interaction_multi}
\end{figure}

@@

\subsection{Interaction Flow}
{\bf Look:} Users select a target device by looking in its general direction.
Glass periodically sends a device id through its IR emitter analogous to Patel's approach~\cite{patel_2-way_2003}. Target appliances have IR receivers and offer immediate visual feedback by toggling a red LED whenever a valid id is received (Figure~\ref{fig:interaction}B). This enables {\em scanning} the environment with ones gaze to see which devices can be controlled.

@@

{\bf Control:} Glass displays a user interface for parameters of the chosen device. The interface is controlled with the temple-mounted touchpad through the following gesture set: tapping toggles discrete parameters; single finger swipe changes between available parameters; double finger swipe adjusts continuous parameters. This scheme was chosen because the touchpad is only comfortably operable in the coronal plane (front to back) but not in the saggital plane (up and down). 
Control commands are sent over XBee radios.

@@

\subsection{Disambiguation}
Head orientation only indicates a general area of visual interest. It does not necessarily match gaze orientation as extra-ocular muscles can move the eyes. The IR beam of our device also has a certain spread (see next section). In an environment dense with potential targets, multiple targets could be within range. Users can tell when multiple feedback LEDs in the environment illuminate (Figure~\ref{fig:interaction_multi}A). To disambiguate, users can either move to adjust their head position, or, alternatively, call up a disambiguation dialog on the Glass display. The dialog presents a list filtered to only those devices that are within IR range, whlie devices also lights up blue led as visual cues. Users navigate the list using the touchpad (Figure~\ref{fig:interaction_multi}B), and then continue their interaction as described above.
